Memo fractal dimension

### 2014-12-17 fig_plis/article_plis.tex
fig:mesh update caption

\begin{figure}
	\includegraphics{mesh}
	\caption{Gel microstructure. (a) Detail of a confocal micrograph of a 4\%w casein, 4\%w GDL in water, when only the slide is coated (not the cover slip). Time corresponds to the minimum in mesh size. Scale bar is \SI{10}{\micro\metre}. (b) Corresponding radial averaged Fourier transform. Black line is the best fit by Eq.XXX with $\xi=\SI{4.9}{\micro\metre}$ and $\gamma=2.4$. Inset shows the center of the non radial average spectrum (arbitrary logarithmic color scale). Scale bar is \SI{10}{\per\micro\metre}. (c-d) Idem in a 50\%w glycerol solvent, with $\xi=\SI{1.5}{\micro\metre}$ and $\gamma=2.5$.}
	\label{fig:mesh}
\end{figure}

>>>>

\begin{figure}
	\includegraphics{mesh}
	\caption{Gel microstructure. (a) Detail of a confocal micrograph of a 4\%w casein, 4\%w GDL in water, when only the slide is coated (not the cover slip). Time corresponds to the minimum in mesh size. Scale bar is \SI{10}{\micro\metre}. (b) Corresponding radial averaged Fourier transform. Black line is the best fit by Eq.XXX with $\xi=\SI{2.0}{\micro\metre}$ and $d_{3D}=2.27$. Inset shows the center of the non radial average spectrum (arbitrary logarithmic color scale). Scale bar is \SI{10}{\per\micro\metre}. (c-d) Idem in a 50\%w glycerol solvent, with $\xi=\SI{0.3}{\micro\metre}$ and $d_{3D}=3$.}
	\label{fig:mesh}
\end{figure}

### 2014-12-17 plis_figures.tex
fig:mesh update caption

\begin{figure}
	\tikzsetnextfilename{mesh}
	\input{fig_plis/mesh.pgf}
	\caption{Gel microstructure. (a) Detail of a confocal micrograph of a 4\%w casein, 4\%w GDL in water, when only the slide is coated (not the cover slip). Time corresponds to the minimum in mesh size. Scale bar is \SI{10}{\micro\metre}. (b) Corresponding radial averaged Fourier transform. Black line is the best fit by Eq.XXX with $\xi=\SI{4.9}{\micro\metre}$ and $d=2.4$. Inset shows the center of the non radial average spectrum (arbitrary logarithmic color scale). Scale bar is \SI{10}{\per\micro\metre}. (c-d) Idem in a 50\%w glycerol solvent, with $\xi=\SI{1.5}{\micro\metre}$ and $d=2.5$.}
	\label{fig:mesh}
\end{figure}

>>>>

\begin{figure}
	\tikzsetnextfilename{mesh}
	\input{fig_plis/mesh.pgf}
	\caption{Gel microstructure. (a) Detail of a confocal micrograph of a 4\%w casein, 4\%w GDL in water, when only the slide is coated (not the cover slip). Time corresponds to the minimum in mesh size. Scale bar is \SI{10}{\micro\metre}. (b) Corresponding radial averaged Fourier transform. Black line is the best fit by Eq.XXX with $\xi=\SI{2.0}{\micro\metre}$ and $d_{3D}=2.27$. Inset shows the center of the non radial average spectrum (arbitrary logarithmic color scale). Scale bar is \SI{10}{\per\micro\metre}. (c-d) Idem in a 50\%w glycerol solvent, with $\xi=\SI{0.3}{\micro\metre}$ and $d_{3D}=3$.}
	\label{fig:mesh}
\end{figure}
